%--------------------------------%
% Author     : Gajanan Choudhary %
% License    : MIT               %
% About file : LaTeX Resume      %
%--------------------------------%

\documentclass[letterpaper,10pt]{article}

\include{mypacks}
\include{mymacros}

\begin{document}

%-----------------------------%
% Customize your resume below %
%-----------------------------%
{\scshape\huge\Author}\vspace{2pt}
%\href{\AuthorWebsiteLink}{\scshape\huge\Author}\vspace{2pt}

\begin{small}
  %Website: \href{\AuthorWebsiteLink}{\color[HTML]{0f4cb4}\myuline{\smash{\AuthorWebsiteText}}}
  Website: \href{\AuthorWebsiteLink}{\AuthorWebsiteText}

  \vspace{2pt}\AuthorAddress

  \vspace{1pt}\href{mailto:\AuthorEmail}{\AuthorEmail} |
  \href{\AuthorPhoneLink}{\AuthorPhoneText}
\end{small}

%------------------------------------SUMMARY-----------------------------------%
\section{Summary}
Software engineer and computational scientist with 8 years of
inter-disciplinary research and software development experience through
15\smallplus{} projects spanning high-performance computing (HPC), applied
mathematics, numerical methods, computational mechanics, optimization, and
machine learning. Creator of 4 scientific software, contributor to 4 HPC
software written in C, \CC{}, DP\CC{}, Python, and Fortran, and author of 5
published technical documents.
%% \\[1\baselineskip] added above since \parbox{0.546\linewidth}{\section{Summary}}
%% messes up line spacing in the new section causing overlapping lines.

%------------------------------------HEADING-----------------------------------%
\vspace{-182.8pt}

\begin{wrapfigure}[-20]{R}{0pt} %{-3cm}

  \centering

  \begin{tikzpicture}[x=1in, y=-1in, every node/.style={right}] 

    \begin{tinyb}

      \node[color=uto]at (0.26,0.13){\footnotesize ANSYS\space };
      
      \node[color=uto]at (0.57,0.25){\tiny CSS\space };

      \node[color=utg]at (0.17,0.34){\Large Python\space };

      \node[color=uto]at (0.38,0.45){\scriptsize Matplotlib\space };

      \node[color=utg]at (0.42,0.58){\normalsize MPI\space };

      \node[color=uto]at (0.29,0.88){\footnotesize Abaqus\space };

      \node[color=utg]at (0.12,1.03){\footnotesize SWIG\space };

      \node[color=uto]at (0.16,1.18){\small CMake\space };

      \node[color=uto]at (0.75,0.19){\normalsize Docker\space };

      \node[color=utg]at (0.85,0.43){\footnotesize Bash\space };

      \node[color=uto]at (0.79,0.57){\footnotesize ctypes\space };

      \node[color=utg]at (0.77,0.89){\footnotesize IIT Kharagpur\space };

      \node[color=uto]at (0.50,1.03){\large CircleCI\space };

      \node[color=utg]at (0.65,1.17){\normalsize Neural Networks\space };

      \node[color=uto]at (1.24,0.14){\footnotesize Image Processing\space };

      \node[color=uto]at (1.07,0.35){\large GitHub\space };

      \node[color=utg]at (1.15,0.50){\scriptsize SVN\space };

      \node[color=uto]at (1.18,1.01){\footnotesize MATLAB\space };

      \node[color=uto]at (1.31,1.11){\tiny HTML\space };

      \node[color=utg]at (1.51,0.22){\tiny STAAD Pro\space };

      \node[color=utg]at (1.66,0.32){\footnotesize Coveralls\space };

      \node[color=uto]at (1.43,0.48){\footnotesize ADCIRC\space };

      \node[color=utg]at (1.36,0.61){\small Fortran\space };

      \node[color=uto]at (1.70,0.92){\normalsize AdH\space };
      
      \node[color=utg]at (1.73,1.06){\small f2py\space };

      \node[color=uto]at (1.76,1.18){\scriptsize ParaView\space };

      \node[color=uto]at (1.99,0.23){\scriptsize Make\space };

      \node[color=uto]at (1.93,0.48){\normalsize Finite Elements\space };

      \node[color=utg]at (2.05,1.03){\huge C/\bigCC{}\space };

      \node[color=utg]at (2.20,0.12){\footnotesize OpenMP\space };

      \node[color=uto]at (2.39,0.21){\scriptsize UT Austin\space };

      \node[color=utg]at (2.16,0.32){\small Travis CI\space };

      \node[color=utg]at (2.49,0.42){\tiny AutoCAD\space };

      \node[color=utg]at (2.26,0.61){\scriptsize ERDC\space };

      \node[color=uto]at (2.65,0.90){\scriptsize Git\space };

      \node[color=uto]at (2.40,1.19){\scriptsize SMS/WMS\space };

    \end{tinyb}

    \node[color=uto]at (0.10,0.74){\huge Computational Scientist\space };

    \draw[color=gray] (current bounding box.north east) -- (current bounding box.north west) -- (current bounding box.south west) -- (current bounding box.south east) -- cycle;

  \end{tikzpicture}

\end{wrapfigure}

\strut{} %% For ending wrapfig wrapping properly

\vspace{169.8pt}

\vspace{-2pt}
%---------------------------------WORK EXPERIENCE------------------------------%
\section{Work Experience}
  \resumeSubHeadingListStart

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Software Engineer}{\dates{February 2021}{Present}}

      %-------------------------------Job 5------------------------------------%
      \resumeSubSubheading{\textbf{Intel Corporation}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Owned sparse linear algebra and sparse solver
            components as a contributor in the
            Intel\textsuperscript{\scriptsize{\textregistered}} oneAPI Math
            Kernel Library (oneMKL) team.}
          \resumeUnlabeledItem{Implemented GPU performance optimizations for the
            newly introduced DP\CC{} API of sparse $\times$ sparse matrix
            product for compressed sparse row (CSR) matrices in oneMKL.}
          \resumeUnlabeledItem{Doubled the performance of block sparse row (BSR)
            matrix $\times$ row-major dense matrix product in oneMKL on CPUs
            by implementing loop unrolling and AVX2/AVX512 compiler intrinsics.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Research Associate}{\dates{December 2020}{February 2021}}
 
      %-------------------------------Job 4------------------------------------%
      \resumeSubSubheading{\textbf{The University of Texas at Austin}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Led the development of coupled PyTorch
            neural network and CFD/physics models in the Python
            software, Water Coupler, to potentially save lives and billions of
            dollars through hurricane compound flood forecasts.}
          \resumeUnlabeledItem{Led software projects that the US Army Corps
            of Engineers (USACE) sponsored to expand the capabilities of
            their CFD software, AdH, through addition of PETSc solvers and
            coupling with HEC-RAS.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Postdoctoral Fellow}{\dates{October 2019}{December 2020}}
 
      %-------------------------------Job 3------------------------------------%
      \resumeSubSubheading{\textbf{The University of Texas at Austin}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Extended Water Coupler by coupling the CFD
            software, ADCIRC and GSSHA, for compound flood forecasts.}
          \resumeUnlabeledItem{Created pyADCIRC, the parallel Python interface
            of ADCIRC, to enable multi-software coupling and physics-based
            machine learning applications with it for improved hurricane
            flood forecasts.}
          \resumeUnlabeledItem{Developed, verified, and validated coupled
            diffusive wave and groundwater models in the CFD software, AdH.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Graduate Research Assistant}{\dates{September 2014}{October 2019}}
 
    %---------------------------------Job 2------------------------------------%
      \resumeSubSubheading{\textbf{The University of Texas at Austin}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Led the creation of 3 new open-source software
            and contributed major modules to 2 existing HPC software through
            4 USACE-sponsored federal projects.}
          \resumeUnlabeledItem{Created the open-source parallel Python software,
            Water Coupler, by coupling 2 CFD software of USACE, AdH and GSSHA,
            to save lives through real-time hurricane compound flood forecasts.}
          \resumeUnlabeledItem{Developed the HPC Python interfaces of AdH and
            GSSHA by creating and using a new open-source software, htopy, which
            automates generation of Python wrappers of C/\CC{} software in
            hours instead of days.}
          \resumeUnlabeledItem{Developed, tested, verified, validated,
            documented, and published coupling between 2D and 3D shallow water
            models in AdH for USACE for enabling one of the first simulations of
            flooding with 3D ocean models.}
          \resumeUnlabeledItem{Created the open-source C software,
            AdH-meshbuilder, for generating arrays of coupled AdH models.}
          \resumeUnlabeledItem{Contributed numerous physics modules to AdH for
            USACE, including its wind library, 3D prism mesh adaption, and
            improved parallel load rebalancing for 3D models.}
       \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Assistant Surveyor}{\dates{July 2013}{July 2014}}
 
      %-------------------------------Job 1------------------------------------%
      \resumeSubSubheading{\textbf{Indian Register of Shipping}}{Mumbai, India}
        \resumeItemListStart
          \resumeUnlabeledItem{Worked on 3 projects on stress response of ships
            to various loads, leading to 1 new software and 1 publication.}
          \resumeUnlabeledItem{Created and documented IR-Sect, a MATLAB software
            with a graphical user interface (GUI) for finite element (FE)
            analysis of 2D ship cross-sections, with capability to translate
            input to ANSYS.}
          \resumeUnlabeledItem{Implemented 2D modeling capabilities in IR-Sect,
            including insert, copy, move, mirror, delete, and AutoCAD-style
            selection operations to reduce modeling time to hours from days.}
          \resumeUnlabeledItem{Implemented graph algorithms in IR-Sect for
            calculating sectorial properties of ship cross-sections to enable
            shear flow, bending, torsion, and warping analysis.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-3pt}

%-----------------------------------PROJECTS-----------------------------------%
\section{Software Contributions}
  \resumeSubItemListStart
    \resumeSubItem{Contributor -- \href{https://https://www.intel.com/content/www/us/en/developer/tools/oneapi/onemkl.html}{Intel\textsuperscript{\scriptsize{\textregistered}} oneAPI Math Kernel Library (oneMKL)}}
      {Owned feature implementations, CPU/GPU architecture-specific performance
       optimizations, and bug fixes for sparse linear algebra and sparse solver
       components in oneMKL, written in \textbf{C}, \textbf{\CC{}},
       \textbf{DP\CC{}}, and \textbf{Fortran}.}
    \resumeSubItem{Creator -- \href{https://github.com/gajanan-choudhary/water-coupler}{Water Coupler}}
      {Developed the \textbf{open-source parallel Python} software for coupling
      physics models, AdH (\textbf{C}), GSSHA (\textbf{\CC{}}), and ADCIRC
      (\textbf{Fortran}), as well as PyTorch machine learning/neural network
      models for real-time hurricane compound flood simulations.}
    \resumeSubItem{Contributor -- \href{https://www.erdc.usace.army.mil/Locations/CHL/AdH/}{AdH}}
      {Created the C/Python interface of AdH (adhpython), enhanced its meteorological library,
      improved mesh adaption, and coupled its shallow water, ground
      water, and diffusive wave models, all in parallel.}
    \resumeSubItem{Contributor -- \href{http://adcirc.org/}{ADCIRC}}
      {Created the Fortran/Python interface of ADCIRC (pyADCIRC), enabling physics
      based machine learning applications and multi-software coupling in Water
      Coupler.}
    \resumeSubItem{Contributor -- \href{https://www.gsshawiki.com/}{GSSHA}}
      {Created the \CC{}/Python interface of GSSHA (gsshapython) enabling
      multi-software coupling with ADCIRC and AdH in Water Coupler.}
    \resumeSubItem{Creator -- \href{https://github.com/gajanan-choudhary/htopy}{htopy}}
      {Developed an \textbf{open-source Python} software for partially
      automating the generation of Python interfaces of \textbf{C/\CC{}}
      software, and used it to generate the Python interfaces of AdH and GSSHA.}
    \resumeSubItem{Creator -- \href{https://github.com/gajanan-choudhary/AdH_meshbuilder}{AdH-meshbuilder}}
      {Developed an \textbf{open-source C} software for generating arrays of
      coupled AdH finite element models.}
    \resumeSubItem{Creator -- IR-Sect}
      {Developed a proprietary \textbf{MATLAB} software with a graphical user
      interface (\textbf{GUI}) for modeling 2D ship cross-sections and
      calculating their sectorial properties by implementing graph algorithms.}
  \resumeSubItemListEnd
\vspace{-5pt}

%------------------------------PROGRAMMING SKILLS------------------------------%
\section{Skills}
  \resumeSubHeadingListStart

    \resumeSubheading{Software development:}{}
      \resumeItemListStart
        \resumeItem{Programming}{C/\CC{}, DP\CC{}, Python, Fortran, MATLAB,
            SYCL, MPI, OpenMP, f2py, SWIG, Python/C API, and Bash.}

        \resumeItem{Tools}{GitHub, Bitbucket, Git, Mercurial, SVN,
            Travis CI, CircleCI, Docker, Coveralls, Codecov, CMake, GNU Make,
            Gcov, LCOV, GProf, GDB, Valgrind, Doxygen, \LaTeX{}, HTML,
            and CSS.}

        \resumeItem{Concepts}{Data structures, algorithms, complexity,
            object-oriented programming (OOP), standard template library (STL),
            high-performance computing, parallel programming, debugging, general
            purpose GPU (GPGPU) programming, language interoperability,
            continuous integration and continuous delivery (CI/CD), and
            test-driven development (TDD).}
      \resumeItemListEnd

    \resumeSubheading{Research:}{}
      \resumeItemListStart
        \resumeItem{Mathematics}
          {Numerical methods, partial differential equations, linear algebra,
          approximation, functional analysis, advanced theory of finite element
          methods, and optimization.}

        \resumeItem{Engineering}
          {Computational mechanics, computational fluid dynamics (CFD), solid
          mechanics, structural dynamics, fluid-structure interaction, and
          coupled numerical models.}

        \resumeItem{Applications}
          {Adaptive Hydraulics (AdH), ADvanced CIRCulation (ADCIRC), Gridded
          Surface Subsurface Hydrologic Analysis (GSSHA), ANSYS, Abaqus,
          ParaView, Aquaveo SMS/WMS, and AutoCAD.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-5pt}

%-----------------------------------EDUCATION----------------------------------%
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading{Doctorate (Ph.D.) in Engineering Mechanics}{\dates{August 2014}{December 2019}}

      \resumeSubSubheading{The University of Texas at Austin}{Austin, TX}

    \resumeSubheading{Graduate Portfolio in Scientific Computing}{\dates{August 2014}{May 2018}}

      \resumeSubSubheading{The University of Texas at Austin}{Austin, TX}

    \resumeSubheading{Master of Science (M.S.) in Engineering Mechanics}{\dates{August 2014}{May 2017}}

      \resumeSubSubheading{The University of Texas at Austin}{Austin, TX}

    \resumeSubheading{Bachelor of Technology (B.Tech.) in Civil Engineering}{\dates{July 2009}{July 2013}}

      \resumeSubSubheading{Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}

  \resumeSubHeadingListEnd
\vspace{-8pt}

%\section{Education}
%  \resumeSubHeadingListStart
%
%    \resumeSubheading{The University of Texas at Austin}{Austin, TX}
%
%      \resumeSubSubheading{Doctorate (Ph.D.) in Engineering Mechanics}{\dates{August 2014}{December 2019}}
%
%      \resumeSubSubheading{Graduate Portfolio in Scientific Computing}{\dates{August 2014}{May 2018}}
%
%      \resumeSubSubheading{Master of Science (M.S.) in Engineering Mechanics}{\dates{August 2014}{May 2017}}
%
%    \resumeSubheading{Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}
%
%      \resumeSubSubheading{Bachelor of Technology (B.Tech.) in Civil Engineering}{\dates{July 2009}{July 2013}}
%
%  \resumeSubHeadingListEnd
%\vspace{-8pt}

%----------------------------INTERNSHIP EXPERIENCE-----------------------------%
\section{Internship Experience}
  \resumeSubHeadingListStart

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Structural Design Intern}{\dates{May 2012}{July 2012}}
 
      %-------------------------------Job 2------------------------------------%
      \resumeSubSubheading{\textbf{Himanshu Tulpule and Associates}}{Pune, India}
        \resumeItemListStart
          \resumeUnlabeledItem{Designed and detailed 14 reinforced
                              concrete and steel structures spanning 7
                              different types, including trusses, frames, slabs,
                              tanks, arches, foundations, and composite beams.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Draftsman Intern}{\dates{May 2010}{June 2010}}
 
      %-------------------------------Job 1------------------------------------%
      \resumeSubSubheading{\textbf{Himanshu Tulpule and Associates}}{Pune, India}
        \resumeItemListStart
          \resumeUnlabeledItem{Created structural drawings of reinforced
                              concrete and steel structures using AutoCAD.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-4pt}

%-----------------------------VOLUNTEER EXPERIENCE-----------------------------%
\section{Volunteer Experience}
  \resumeSubHeadingListStart

    %---------------------------------Title------------------------------------%
    \resumeSubheading{GLUE Mentor}{\dates{January 2018}{May 2018}}
 
      %-------------------------------Job 3------------------------------------%
      \resumeSubSubheading{\textbf{The University of Texas at Austin}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Mentored an undergraduate student at UT
            Austin in Spring '18 in support of the Women in Engineering
            Program's mission of inspiring women to pursue graduate degrees in
            STEM.}
          \resumeUnlabeledItem{Directed a semester-long research project for the
            mentee to train her in research through bi-weekly meetings for
            training, discussing progress, and providing guidance.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Undergraduate Research Assistant}{\dates{March 2012}{July 2013}}
 
      %-------------------------------Job 2------------------------------------%
      \resumeSubSubheading{\textbf{Indian Institute of Technology (IIT) Kharagpur}}{Kharagpur, India}
        \resumeItemListStart
          \resumeUnlabeledItem{Published a peer-reviewed paper on detecting
            cracks in concrete using an image processing and neural network
            model that achieved 98.8\% accuracy, 99.7\% specificity,
            80\% precision, and 60\% sensitivity.}
          \resumeUnlabeledItem{Proposed improvements to genetic algorithms for
            optimization of truss weights, establishing new minima for 3
            benchmark problems in literature.}
          \resumeUnlabeledItem{Supported the research of a PhD student by
            creating finite element models and simulations of sandwich materials
            subject to under-water blasts.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Publicity Team Member, Megalith '11}{\dates{July 2010}{December 2011}}
 
      %-------------------------------Job 1------------------------------------%
      \resumeSubSubheading{\textbf{Indian Institute of Technology (IIT) Kharagpur}}{Kharagpur, India}
        \resumeItemListStart
          \resumeUnlabeledItem{Contributed in increasing the number of
            participants in Megalith '11, the annual technical festival of the
            civil engineering department, by 25\% compared to the prior year by
            promoting the festival on social media and visiting and inviting
            students from multiple universities across India.}
          \resumeUnlabeledItem{Handled participant registration and guest
            reception during the festival, and played an advisory role in the
            team of the following year's festival, Megalith '12.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-4pt}

%----------------------------------ACTIVITIES----------------------------------%
\section{Activities}
  \resumeSubHeadingListStart
    \resumeSubItem{Teaching}{Obtained a \textbf{basic teaching certificate} by
                            attending a teaching workshop series at UT Austin.}
    \resumeSubItem{Dance}{Completed intermediate level training in social dance
                         forms at UT Austin and Austin Swing Syndicate.}
    \resumeSubItem{Music}{Trained in classical piano at UT Austin and performed
                         as a drummer in events at IIT Kharagpur.}
    \resumeSubItem{Theatre}{Performed in plays at IIT Kharagpur as a member of
                           the English Technology Dramatics Society.}
  \resumeSubHeadingListEnd

%------------------------------------THESES------------------------------------%
\begin{refsection}
\section{Theses}
\nocite{*}                          % cite everything
\printbibliography[heading = none,  % no heading (e.g., "References")
keyword = thesis,                   % FILTER BY < article > KEYWORD
check = recent, 
env = mybib]                        % Use mybib style
\end{refsection}
\vspace{-10pt}

%--------------------------PEER-REVIEWED PUBLICATIONS--------------------------%
\begin{refsection}
\section{Peer-reviewed Publications}
\nocite{*}                          % cite everything
\printbibliography[heading = none,  % no heading (e.g., "References")
keyword = article,                  % FILTER BY < article > KEYWORD
check = recent, 
env = mybib]                        % Use mybib style
\end{refsection}
\vspace{-10pt}

%---------------------------------OTHER REPORTS--------------------------------%
\begin{refsection}
\section{Other Reports}
\nocite{*}                          % cite everything
\printbibliography[heading = none,  % no heading (e.g., "References")
keyword = report,                   % FILTER BY < article > KEYWORD
check = recent, 
env = mybib]                        % Use mybib style
\end{refsection}
\vspace{-10pt}

%--------------------------------------TALKS-----------------------------------%
\begin{refsection}
\section{Talks}
\nocite{*}                          % cite everything
\printbibliography[heading = none,  % no heading (e.g., "References")
keyword = talk,                     % FILTER BY < article > KEYWORD
check = recent, 
env = mybib]                        % Use mybib style
\end{refsection}

%-----------------------------------SELECT WORKS-------------------------------%
%\begin{refsection}
%\section{Select Works}
%\nocite{*}                          % cite everything
%\printbibliography[heading = none,  % no heading (e.g., "References")
%keyword = select,                   % FILTER BY < article > KEYWORD
%check = recent, 
%env = mybib]                        % Use mybib style
%\end{refsection}

%------------------------------------THE END-----------------------------------%
\end{document}
