%--------------------------------%
% Author     : Gajanan Choudhary %
% License    : MIT               %
% About file : LaTeX Resume      %
%--------------------------------%

\documentclass[letterpaper,10pt]{article}

\include{mypacks}
\include{mymacros}

\begin{document}

%-----------------------------%
% Customize your resume below %
%-----------------------------%
{\scshape\huge\Author}\vspace{2pt}
%\href{\AuthorWebsiteLink}{\scshape\huge\Author}\vspace{2pt}

\begin{small}
  %Website: \href{\AuthorWebsiteLink}{\color[HTML]{0f4cb4}\myuline{\smash{\AuthorWebsiteText}}}
  Website: \href{\AuthorWebsiteLink}{\AuthorWebsiteText}

  \vspace{2pt}\AuthorAddress

  \vspace{1pt}\href{mailto:\AuthorEmail}{\AuthorEmail} |
  \href{\AuthorPhoneLink}{\AuthorPhoneText}
\end{small}

%------------------------------------SUMMARY-----------------------------------%
\section{Summary}
Computational scientist and software engineer with over 10 years of
inter-disciplinary research and software development experience spanning
high-performance computing (HPC), applied mathematics, computational
mechanics, performance optimization, and machine learning. Creator of 4
scientific software, contributor to 5 HPC software written in C, \CC{},
SYCL/DP\CC{}, Python, and Fortran, and author of 5 published technical
documents.

%------------------------------------HEADING-----------------------------------%
\vspace{-182.8pt}

\begin{wrapfigure}[-20]{R}{0pt} %{-3cm}

  \centering

  \begin{tikzpicture}[x=1in, y=-1in, every node/.style={right}] 

    \begin{tinyb}

      \node[color=utg]at (0.20,0.13){\footnotesize Assembly\space };

      \node[color=uto]at (0.10,0.20){\tiny Kernels\space };

      \node[color=uto]at (0.57,0.25){\tiny Docker\space };

      \node[color=utg]at (0.17,0.34){\Large Python\space };

      \node[color=uto]at (0.46,0.45){\scriptsize Sparse BLAS\space };

      \node[color=utg]at (0.08,0.51){\footnotesize ANSYS\space };

      \node[color=utg]at (0.47,0.61){\normalsize MPI\space };

      \node[color=uto]at (0.09,0.92){\scriptsize Intel Corporation\space };

      \node[color=utg]at (0.12,1.03){\footnotesize SWIG\space };

      \node[color=uto]at (0.16,1.18){\small CMake\space };

      \node[color=uto]at (0.78,0.17){\large SYCL\space };

      \node[color=utg]at (0.85,0.32){\tiny GPUs\space };

      \node[color=uto]at (0.79,0.57){\footnotesize ctypes\space };

      \node[color=utg]at (0.85,0.89){\footnotesize IIT Kharagpur\space };

      \node[color=uto]at (0.50,1.03){\large CircleCI\space };

      \node[color=utg]at (0.65,1.17){\normalsize Neural Networks\space };

      \node[color=uto]at (1.28,0.14){\footnotesize Image Processing\space };

      \node[color=utg]at (1.25,0.22){\tiny Performance optimization\space };

      \node[color=uto]at (1.07,0.35){\large GitHub\space };

      \node[color=utg]at (1.10,0.50){\scriptsize HPCG\space };

      \node[color=uto]at (1.18,1.01){\footnotesize MATLAB\space };

      \node[color=uto]at (1.31,1.11){\tiny Bash\space };

      \node[color=utg]at (1.66,0.32){\footnotesize Coveralls\space };

      \node[color=uto]at (1.43,0.48){\footnotesize ADCIRC\space };

      \node[color=utg]at (1.36,0.61){\small Fortran\space };

      \node[color=utg]at (1.60,0.87){\tiny CPUs\space };

      \node[color=uto]at (1.77,0.92){\normalsize AdH\space };

      \node[color=utg]at (1.73,1.06){\small f2py\space };

      \node[color=uto]at (1.76,1.18){\scriptsize ParaView\space };

      \node[color=utg]at (2.20,0.12){\footnotesize OpenMP\space };

      \node[color=uto]at (2.08,0.23){\scriptsize Make\space };

      \node[color=uto]at (2.39,0.21){\scriptsize UT Austin\space };

      \node[color=utg]at (2.16,0.32){\small Travis CI\space };

      \node[color=utg]at (2.33,0.40){\tiny Compiler Intrinsics\space };

      \node[color=uto]at (1.93,0.50){\normalsize Applied Math\space };

      \node[color=utg]at (2.26,0.61){\scriptsize ERDC\space };

      \node[color=uto]at (2.65,0.90){\scriptsize Git\space };

      \node[color=utg]at (2.05,1.03){\huge C/\bigCC{}\space };

      \node[color=uto]at (2.40,1.19){\scriptsize SMS/WMS\space };

    \end{tinyb}

    \node[color=uto]at (0.10,0.74){\huge Computational Scientist\space };

    \draw[color=gray] (current bounding box.north east) -- (current bounding box.north west) -- (current bounding box.south west) -- (current bounding box.south east) -- cycle;

  \end{tikzpicture}

\end{wrapfigure}

\strut{} %% For ending wrapfig wrapping properly

\vspace{169.8pt}

\vspace{-2pt}
%---------------------------------WORK EXPERIENCE------------------------------%
\section{Work Experience}
  \resumeSubHeadingListStart

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Software Engineer}{\dates{February 2021}{Present}}

      %-------------------------------Job 5------------------------------------%
      \resumeSubSubheading{\textbf{Intel Corporation}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Owned sparse linear algebra and high-performance
            conjugate gradient (HPCG) benchmark components as a contributor in
            the Intel\textsuperscript{\scriptsize{\textregistered}} oneAPI Math
            Kernel Library (oneMKL) team.}
          \resumeUnlabeledItem{Doubled the performance of sparse matrix-vector
            product (GEMV) oneMKL SYCL API on latest Intel GPUs using SIMD
            vectorization and prefetching techniques.}
          \resumeUnlabeledItem{Implemented GPU performance optimizations for
            the newly introduced sparse $\times$ sparse matrix product
            (matmat/spGEMM) SYCL API for compressed sparse row (CSR) matrices
            in oneMKL.}
          \resumeUnlabeledItem{Doubled the performance of block sparse row (BSR)
            matrix $\times$ row-major dense matrix product in oneMKL on CPUs
            by using AVX512 compiler intrinsics.}
          \resumeUnlabeledItem{Introduced optimized SYCL APIs in oneMKL
            for sorting, copying and transposing CSR matrices on GPUs.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Research Associate}{\dates{December 2020}{February 2021}}
 
      %-------------------------------Job 4------------------------------------%
      \resumeSubSubheading{\textbf{The University of Texas at Austin}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Led the development of coupled PyTorch
            neural network and CFD/physics models in the Python
            software, Water Coupler, to potentially save lives and billions of
            dollars through hurricane compound flood forecasts.}
          \resumeUnlabeledItem{Led software projects that the US Army Corps
            of Engineers (USACE) sponsored to expand the capabilities of
            their CFD software, AdH, through addition of PETSc solvers and
            coupling with HEC-RAS.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Postdoctoral Fellow}{\dates{October 2019}{December 2020}}
 
      %-------------------------------Job 3------------------------------------%
      \resumeSubSubheading{\textbf{The University of Texas at Austin}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Extended Water Coupler by coupling the CFD
            software, ADCIRC and GSSHA, for compound flood forecasts.}
          \resumeUnlabeledItem{Created pyADCIRC, the parallel Python interface
            of ADCIRC, to enable multi-software coupling and physics-based
            machine learning applications with it for improved hurricane
            flood forecasts.}
          \resumeUnlabeledItem{Developed, verified, and validated coupled
            diffusive wave and groundwater models in the CFD software, AdH.}
        \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Graduate Research Assistant}{\dates{September 2014}{October 2019}}
 
    %---------------------------------Job 2------------------------------------%
      \resumeSubSubheading{\textbf{The University of Texas at Austin}}{Austin, TX}
        \resumeItemListStart
          \resumeUnlabeledItem{Led the creation of 3 new open-source software
            and contributed major modules to 2 existing HPC software through
            4 USACE-sponsored federal projects.}
          \resumeUnlabeledItem{Created the open-source parallel Python software,
            Water Coupler, by coupling 2 CFD software of USACE, AdH and GSSHA,
            to save lives through real-time hurricane compound flood forecasts.}
          \resumeUnlabeledItem{Developed, tested, verified, validated,
            documented, and published coupling between 2D and 3D shallow water
            models in AdH for USACE for enabling one of the first simulations of
            flooding with 3D ocean models.}
          \resumeUnlabeledItem{Developed important physics features in AdH
            for USACE, including its wind library, 3D prism mesh adaption,
            and improved parallel load rebalancing in 3D models.}
       \resumeItemListEnd

    %---------------------------------Title------------------------------------%
    \resumeSubheading{Assistant Surveyor}{\dates{July 2013}{July 2014}}
 
      %-------------------------------Job 1------------------------------------%
      \resumeSubSubheading{\textbf{Indian Register of Shipping}}{Mumbai, India}
        \resumeItemListStart
          \resumeUnlabeledItem{Worked on 3 projects on stress response of ships
            to various loads, leading to 1 new software and 1 publication.}
          \resumeUnlabeledItem{Created and documented IR-Sect, a MATLAB software
            with a graphical user interface (GUI) for finite element (FE)
            analysis of 2D ship cross-sections, with capability to translate
            input to ANSYS.}
          \resumeUnlabeledItem{Implemented 2D modeling capabilities in IR-Sect,
            including insert, copy, move, mirror, delete, and AutoCAD-style
            selection operations to reduce modeling time to hours from days.}
          \resumeUnlabeledItem{Implemented graph algorithms in IR-Sect for
            calculating sectorial properties of ship cross-sections to enable
            shear flow, bending, torsion, and warping analysis.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-3pt}

%-----------------------------------PROJECTS-----------------------------------%
\section{Select Software Contributions}
  \resumeSubItemListStart
    \resumeSubItem{Contributor -- \href{https://https://www.intel.com/content/www/us/en/developer/tools/oneapi/onemkl.html}{Intel\textsuperscript{\scriptsize{\textregistered}} oneAPI Math Kernel Library (oneMKL)}}
      {Owned feature implementations and CPU/GPU architecture-specific
       performance optimizations for sparse linear algebra and HPCG benchmark
       components in oneMKL, written in \textbf{C}, \textbf{\CC{}},
       \textbf{SYCL/DP\CC{}}, and \textbf{Fortran}.}
    \resumeSubItem{Creator -- \href{https://github.com/gajanan-choudhary/water-coupler}{Water Coupler}}
      {Developed the \textbf{open-source parallel Python} software for coupling
      physics models, AdH (\textbf{C}), GSSHA (\textbf{\CC{}}), and ADCIRC
      (\textbf{Fortran}), as well as PyTorch machine learning/neural network
      models for real-time hurricane compound flood simulations.}
    \resumeSubItem{Contributor -- \href{https://www.erdc.usace.army.mil/Locations/CHL/AdH/}{AdH}}
      {Created the C/Python interface of AdH (adhpython), enhanced its meteorological library,
      improved mesh adaption, and coupled its shallow water, ground
      water, and diffusive wave models, all in parallel.}
    \resumeSubItem{Contributor -- \href{http://adcirc.org/}{ADCIRC}}
      {Created the Fortran/Python interface of ADCIRC (pyADCIRC), enabling physics
      based machine learning applications and multi-software coupling in Water
      Coupler.}
  \resumeSubItemListEnd
\vspace{-5pt}

%------------------------------PROGRAMMING SKILLS------------------------------%
\section{Skills}
  \resumeSubHeadingListStart

    \resumeSubheading{Software development:}{}
      \resumeItemListStart
        \resumeItem{Programming}{C/\CC{}, SYCL/DP\CC{}, Python, Fortran,
            MATLAB, MPI, OpenMP, f2py, SWIG, Python/C API, and Bash.}

        \resumeItem{Tools}{GitHub, Bitbucket, Git, Mercurial, SVN,
            Travis CI, CircleCI, Docker, Coveralls, Codecov, CMake, GNU Make,
            Gcov, LCOV, GProf, GDB, Valgrind, Doxygen, \LaTeX{}, HTML,
            and CSS.}

        \resumeItem{Concepts}{Data structures, algorithms, complexity,
            object-oriented programming (OOP), standard template library (STL),
            parallel programming, CPU and GPU performance optimization,
            language interoperability, continuous integration and
            continuous delivery (CI/CD), and test-driven development (TDD).}
      \resumeItemListEnd

    \resumeSubheading{Research:}{}
      \resumeItemListStart
        \resumeItem{Mathematics}
          {Numerical methods, partial differential equations, linear algebra,
          approximation, functional analysis, advanced theory of finite element
          methods, and optimization.}

        \resumeItem{Engineering}
          {Computational mechanics, computational fluid dynamics (CFD), solid
          mechanics, structural dynamics, fluid-structure interaction, and
          coupled numerical models.}

        \resumeItem{Applications}
          {Adaptive Hydraulics (AdH), ADvanced CIRCulation (ADCIRC), Gridded
          Surface Subsurface Hydrologic Analysis (GSSHA), ANSYS, Abaqus,
          ParaView, Aquaveo SMS/WMS, and AutoCAD.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-5pt}

%-----------------------------------EDUCATION----------------------------------%
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading{The University of Texas at Austin}{Austin, TX}

      \resumeSubSubheading{Doctorate (Ph.D.) in Engineering Mechanics}{\dates{August 2014}{December 2019}}

      \resumeSubSubheading{Graduate Portfolio in Scientific Computing}{\dates{August 2014}{May 2018}}

      \resumeSubSubheading{Master of Science (M.S.) in Engineering Mechanics}{\dates{August 2014}{May 2017}}

    \resumeSubheading{Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}

      \resumeSubSubheading{Bachelor of Technology (B.Tech.) in Civil Engineering}{\dates{July 2009}{July 2013}}

  \resumeSubHeadingListEnd
\vspace{-8pt}

%------------------------------------THE END-----------------------------------%
\end{document}
